The Three-HITs Theorem\footnote{This work was partially supported by COST Action CA15123.}

### 2017-03-22 Paper/Paper.tex
Added small abstract

\begin{abstract}
Lorem ipsum dolor sit amet, consectetur adipiscing elit. Praesent convallis orci arcu, eu mollis dolor. Aliquam eleifend suscipit lacinia. Maecenas quam mi, porta ut lacinia sed, convallis ac dui. Lorem ipsum dolor sit amet, consectetur adipiscing elit. Suspendisse potenti. 
 \end{abstract}

>>>>

\begin{abstract}
We show that all higher inductive types can be constructed from coequalizers, path coequalizers and homotopy colimits.
The proof is inspired by Ad\'amek's theorem which constructs inductive types as a colimit of a functor.
This way one can reason about all higher inductive types by instead studying a small number of examples.
 \end{abstract}
